Verifying Demonstrations

### 2019-07-02 paper/DB-anon-cred.tex
Fixes section titles, moves formal stuff
Puts labels on definitions (distance-bounding)
Adds theorem and proof draft for MF

The \(\UWBPR\) prevents \iac{DBMF} adversary from performing a 
distance-reduction through \iac{DBEDLC} attack~\cite{UWBPR}.
Thus, any relaying will be detected.
The adversary could guess the challenge chosen, \(i\), request \(s_i\) from the 
prover and guess \(s_j\) for \(i\neq j\).
The success probability of this is \(\frac{1}{k} + \frac{k}{q}\) per round, 
thus \((\frac{q + k}{kq})^n\) in total.

@@

\NewAlgorithm{\adv}{A}

@@

\subsection{Achieving \acl{DBDF} resistance}

@@

\subsection{Formal Verification}

>>>>

The \(\UWBPR\) prevents \iac{DBMF} adversary from performing a 
distance-reduction through \iac{DBEDLC} attack~\cite{UWBPR}.
Thus, any relaying will be detected, \ie this justifies \cref{TaintedMF}.

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv)\) is negligible.
\end{theorem}

\begin{proof}
  The adversary has two options:
  \begin{enumerate*}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, this yields a success with probability 
    \(\frac{1}{k}\);
  \item guess the response, this yields success with probability 
    \(\frac{1}{q}\).
  \end{enumerate*}
  The total success probability is \(\frac{1}{k} + \frac{1}{q}\) per round, 
  thus \((q + k)^n (kq)^{-n}\) in total.
  We have that \(k \in \log(\lambda)\), \(q \in \poly[\lambda]\) and it follows 
  that the success probability is negligible,
  \[
    \left( \frac{\log(\lambda) + 
        \poly[\lambda]}{\log(\lambda)\poly[\lambda]}\right)^n \approx
    \frac{1}{\log(\lambda)^n} < \frac{1}{\poly[\lambda]}
  \] for \(n > 2\).
\end{proof}

@@

@@

\subsection{Achieving \acs*{DBDF} resistance}

@@

\subsection{Formal verification}
